Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-01 doc/main_jfm.tex
first pass at section 4

In order to examine the hydrodynamics interactions of JP vesicles, it is
necessary to have a suitable, initial, equilibrium vesicle.  This is
ensures that the dynamics of the bilayer under a shear flow, for
example, reach consistent outcomes.  For our target vesicle, we start
with $N=58$ JP arranged in two circular, apposing monolayers of about
$8$ length units. The directors of outer monolayer point inward and the
directors of the inner monolayer point outward (Figure~\ref{figure2}a).
The JP of this chosen configuration are generally not in equilibrium.
Rather, the inter-particle distances and orientations must make slight
adjustments so that attraction and repulsion are balance.
Figure~\ref{figure2}(b) shows that the magnitudes of the mean velocity
components ${\bf v}=\{v_x,v_y\}$ and the variation $\Delta \theta$ of
the particle orientation decrease exponentially with an approximation
decaying rate $\sim0.005$.  A local energy minimum and the equilibrium
configuration is therefore rapidly attained.  The equilibrium
configuration in Figure~\ref{figure2}a is slightly elliptical.  The
equilibrium eccentricity vanishes for larger $N_b$
(Figure~\ref{figure2}e).

\subsection{Permeability}
Figures~\ref{figure2}c, d demonstrates that the initial, non-equilibrium configuration has a large internal fluid pressure
that vanishes as the configuration tends toward the equilibrium state.  
This suggests that the initial collection of JP is under tension and this tension is relaxed as fluid is expelled through the inter-particle spacing. 
To make a comparison with membrane continuum mechanics, 
lipid bilayer membranes have a large area modulus $K_A$ of about $240$ pN nm$^{-1}$ \cite{NAGLE} 
and changes in surface area give rise to a membrane tension
$\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the membrane surface area and $A_0$ is the reference surface area in the non-tensed state. 
In the two-dimensional vesicles, the tension becomes 
\begin{equation}
\label{eq:stretch}
\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right).
\end{equation}
where $L$ and $L_0$ are the vesicle arc length and resting length, respectively. 
A stretched, circular vesicles has a Laplace pressure 
\begin{equation}
\label{eq:LaplacePressure}
\Delta p = \frac{\tilde \gamma}{R} 
\end{equation}
where $\Delta p$ is the difference in internal pressure to the pressure at infinity
and $R$ is the radius of the circular vesicle.  The factor 
$R^{-1}$ is the total curvature since  the principle curvature in the direction of the cylinder is zero.

\begin{figure}
\centering
\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
  \caption{JP vesicle are suspended in a quiescent flow for relaxations where the reference arc lengths $L_0$ are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm, $2.5$ nm, and $1.25$ nm, respectively. (a) The arc length $L$ decreases over time where the dashed curves represent the data and solid curves are linear fits; (b) A linear relationship between $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels (b) and (c), the cross and asterisk symbols are numerical results and fitted by using solid lines.}
    \label{figure:permeability}
\end{figure}

The particles in our setup do not abut but rather have small gaps due to repulsive forces.
The gaps allow for some fluid flux across the JP bilayer. 
In membrane mechanics, aqueous flux is quantified the equation
\begin{equation}
\label{eq:perm}
\frac{dA}{dt} = -P  L \Delta p.
\end{equation}
where $P$ is a hydraulic permeability constant \cite{CHABANON, QGY-Y}.

The JP vesicle data is in complete agreement with the continuum mechanical model \eqref{eq:stretch}-\eqref{eq:perm_solution}.
In Figure \ref{figure:permeability}, we considered three configurations: a configuration with 58 particles 
($L_0 = 107$ nm, plus symbols); a configuration with 119 particles ($L_0 = 218$ nm, asterick symbols);
and finally a configuration with 117 particles but with diameter 1.25 nm rather than the usual 2.5 nm ($L_0 = 141$ nm, times symbols).
Here $A$ and $L$ refer to the area and length of the mid plane curve separating the inner and outer monolayers. 
(The values for $L_0$ are the asymptotic values for $L$ in Figure \ref{figure:permeability}c).

>>>>

In order to examine the hydrodynamics interactions of JP vesicles, it is
necessary to have a suitable, initial, JP equilibrium vesicle. This
ensures that the dynamics of the bilayer under a shear flow, for
example, reach consistent outcomes. For our target vesicle, we start
with $N=58$ JP arranged in two circular, apposing monolayers of about
$8$ length units. The directors of the outer monolayer point inward and
the directors of the inner monolayer point outward
(Figure~\ref{figure2}a).  The JP of this chosen configuration are
generally not in equilibrium.  Rather, the inter-particle distances and
orientations must make slight adjustments so that attraction and
repulsion balance.  Figure~\ref{figure2}(b) shows that the magnitudes of
the mean velocity components ${\bf v}=\{v_x,v_y\}$ and the variation
$\Delta \theta$ of the particle orientation decrease exponentially with
an approximation decaying rate $\sim0.005$. A local energy minimum and
the equilibrium configuration is therefore rapidly attained. The
equilibrium configuration in Figure~\ref{figure2}a is slightly
elliptical. The equilibrium eccentricity vanishes for larger $N_b$
(Figure~\ref{figure2}e).

\subsection{Permeability}
Figures~\ref{figure2}c and~\ref{figure2}d demonstrate that the initial, non-equilibrium configuration has a large internal fluid pressure
that vanishes as the configuration tends toward the equilibrium state.  
This suggests that the initial collection of JP is under tension and
this tension is relaxed as fluid is expelled through the inter-particle
spacing. To make a comparison with membrane continuum mechanics, lipid
bilayer membranes have a large area modulus $K_A$ of about $240$ pN
nm$^{-1}$ \cite{NAGLE} and changes in surface area give rise to a
membrane tension $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the
membrane surface area and $A_0$ is the reference surface area in the
non-tensed state. In the two-dimensional vesicles, the tension becomes
\begin{align}
\label{eq:stretch}
\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
\end{align}
where $L$ and $L_0$ are the vesicle arc length and resting length,
respectively. A stretched, circular vesicles has a Laplace pressure 
\begin{align}
\label{eq:LaplacePressure}
\Delta p = \frac{\tilde \gamma}{R},
\end{align}
where $\Delta p$ is the difference in internal pressure to the pressure
at infinity and $R$ is the radius of the circular vesicle. The factor
$R^{-1}$ is the total curvature since the principle curvature in the
direction of the cylinder is zero.

\begin{figure}
\centering
\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
  \caption{\label{figure:permeability} JP vesicles are suspended in a
  quiescent flow for relaxations where the reference arc lengths $L_0$
  are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm,
  $2.5$ nm, and $1.25$ nm, respectively. (a) The arc length $L$
  decreases over time where the dashed curves represent the data and
  solid curves are linear fits; (b) A linear relationship between
  $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear
  relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels
  (b) and (c), the cross and asterisk symbols are numerical results and
  fitted by using solid lines.}
\end{figure}

The particles in our setup do not abut but rather have small gaps due to
repulsive forces.  The gaps allow for some fluid flux across the JP
bilayer.  In membrane mechanics, aqueous flux is quantified the equation
\begin{equation} \label{eq:perm} \frac{dA}{dt} = -P  L \Delta p.
\end{equation} where $P$ is a hydraulic permeability constant
\cite{CHABANON, qua-gan-you2021}.

The JP vesicle data is in complete agreement with the continuum
mechanical model~\eqref{eq:stretch}-\eqref{eq:perm_solution}.  In
Figure~\ref{figure:permeability}, we considered three configurations: a
configuration with 58 particles ($L_0 = 107$ nm, plus symbols); a
configuration with 119 particles ($L_0 = 218$ nm, asterick symbols); and
finally a configuration with 117 particles but with diameter 1.25 nm
rather than the usual 2.5 nm ($L_0 = 141$ nm, times symbols).  Here $A$
and $L$ refer to the area and length of the mid plane curve separating
the inner and outer monolayers.  (The values for $L_0$ are the
asymptotic values for $L$ in Figure \ref{figure:permeability}c).
